Numerical investigation of two-phase flow in high-permeability porous media Effect of permeability variation on the surface force between phases

### 2020-04-01 draft.tex
Updates from Overleaf
minor

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdftitle={Numerical investigation of two-phase flow in high-permeability porous media Effect of permeability variation on traction terms},
            pdfauthor={Maxime Cochennec¹; Hossein Davarzani¹* (h.davarzani@brgm.fr); Yohan Davit²; Ioannis Ignatiadis¹; Michel Quintard²},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
% Fix footnotes in tables (requires footnote package)
\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{longtable}}{}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\title{Numerical investigation of two-phase flow in high-permeability porous
media Effect of permeability variation on traction terms}
\author{Maxime Cochennec¹ \and Hossein Davarzani¹* (h.davarzani@brgm.fr) \and Yohan Davit² \and Ioannis Ignatiadis¹ \and Michel Quintard²}
\date{\today{}}

@@

In this paper we study the effects of varying permeability on traction
terms exerted at the different boundaries for two-phase flow in
Hele-Shaw cell. The traction terms, or surface force, are. surface
integrals that are necessary to close the continuous macroscopic
momentum balance equations for two-phase flow in porous media. These
terms are usually modeled from experimental results or obtained by
solving a closure problem (a set of boundary value problems to solve on
a representative periodic unit-cell). Here these terms are calculated
directly by means of direct numerical simulations, and the value of
these terms on each interface is studied as a function of the varying
permeability and capillary number. We focus on two-phase displacement in
high-permeability porous media for which the characteristic flow regimes
implies a non-negligible extent of the fluid-fluid interface and thus;

@@

where the relative velocity is given by \(U_r=U_g-\frac{S_g}{S_l}U_l\)
and \(A_{lg}\) and \(B_{lg}\) are coefficients that depend on the volume
fraction of the gas phase and the medium properties. The subscripts
\(g\) and \(l\) denote the gas phase and the liquid phase, respectively.
This type of model with explicit account of interaction between fluids,
see also
{[}{[}\protect\hyperlink{ref-tung1988hydrodynamic}{33}{]};iliuta2005modelling{]},
gives good results when compared with experimental results
{[}\protect\hyperlink{ref-wang2013modelling}{34}{]}.

@@

@@

As said, an essential step in order to derive some macroscopic law at
macroscale from the microscale is to use averaged quantities to express
the boundary intergals terms that arising because of the averaging
theorem application {[}\protect\hyperlink{ref-Whitaker2013}{35}{]}.
Remember that these closure relations are not presented here but rather
we leave intact the surface integrals, the averaged momentum balance
equations +\textbf{???} for two fluids \(w\) and \(o\), are recast as

@@

\[
u=-\frac{1}{2\mu}\frac{dp}{dx}z(z-h).
\] \{\#eq:poiseuilleProfile\}

@@

There is therefore a direct analogy between flows in a 2D porous medium
and flow in a Hele-Shaw cell, as can be seen in +\textbf{???}, where the
permeability is given by \(h^{2}/12\)
{[}\protect\hyperlink{ref-saffman1958penetration}{36}{]}.

@@

where \(\gamma\) denotes the surface tension and \(\kappa_{\parallel}\)
the curvature in the Hele-Shaw plane
{[}\protect\hyperlink{ref-saffman1958penetration}{36}{]}. The
+\textbf{???} was completed in
{[}\protect\hyperlink{ref-park1984two}{37}{]} by an additional term that
pertains for dynamic film formation and a corrective \(\pi/4\) factor
for the curvature in the cell plane. The reader is warnes that while
dynamic film formation along the plates is an important phenomenom
regarding the flow {[}\protect\hyperlink{ref-jackson2015dynamic}{38}{]},
this requires dedicated study and is beyond the scope of this article.
Thus, we consider in the following that the invading fluid is in contact
with the cell plates, i.e.~presence of a triple line.

@@

In this equation, \(\mathbf{u}\) is the velocity field, \(\tau\) and
\(\psi\) are two numerical parameters that control the diffuse interface
thickness and the amount of reinitialization of the \(\phi\) function,
respectively
{[}\protect\hyperlink{ref-Olsson2005}{39},\protect\hyperlink{ref-Olsson2007}{40}{]}.

@@

where \(k=\frac{\sqrt{12}}{h}\) is an additional term that pertain to a
Darcy-term arising from the depth-averaging of the Stokes equation, as
described in the theoretical background section and \(\mathbf{F}_{st}\)
is the capillary contribution. The capillary contribution is difficult
to compute in volumetric methods such as Level Set and is itself the
object of a large body of work
{[}\protect\hyperlink{ref-Popinet2018}{41}{]}, this term is defined here
as

@@

where \(\gamma\) is the surface tension, \(\kappa\) is the interface
mean curvature, \(\mathbf{n}\) denotes the unit normal to the interface
and \(\delta(\phi)\) is the Dirac delta function localized on the
interface {[}\protect\hyperlink{ref-Galusinski2008}{42}{]}. In this
framework the unit normal vector as well as the mean curvature are
obtained with the level set function \(\phi\) as

@@

respectively, where the \(\pi/4\) correction was derived in
{[}\protect\hyperlink{ref-park1984two}{37}{]} and
\(\kappa_{\perp}=\frac{2}{h}\) is the out-of-plane curvature as
described previously in the theoretical background section.

@@

Let us now sum up all the traction terms and answer the question of the
share of traction exerted on the fluid-fluid boundaries in total
traction. The ratio \(T_{int}^x/T_{s}^x\) is given as a function of the
dimensionless aperture between the Hele-Shaw plates in
\cref{fig:ratioDrag}. The traction exerted on the fluid-fluid boundary
reaches between 10 and 50\% of the traction exerted on the solid-fluid
boundaries. Interestingly, the ratio varies non-monotonically with
\(h^*\), the minimum is reached for the smallest capillary numbers and a
medium range of the aperture values.

Variations with aperture between plates are amplified as the capillary
number decreases. Thus, it is for the lowest capillary number tested
that we obtain both the maximum and minimu m values of the ratio
\(T_{int}^x/T_{s}^x\).

@@

@@

In this work, we investigated the effect of varied permeability on
cocurrent two-phase flow in a Hele-Shaw cell. We focused on the value of
the traction terms, that are necessary to close the macroscopic flow
equations. The idea of solving modified 2D-Stokes equations with a
supplementary Darcy term allowed us to modify the intrinsic permeability
of the structure without having to modify the geometry per se. The range
of intrinsic permeability values investigated is typical of
high-permeability porous media, for which it is known that the flow
regimes are characterized by the large extent of the fluid-fluid
interface (e.g.~film flow). With direct numerical simulations we found
that

@@

The code is validated by comparison with a Boundary-Element Method,
which relies on a surface discretization of the interface and a
pseudo-analytical formulation in the bulk of the phases. This allows us
to precisely locate the interface, even in the case of very thin film
flow, and to carefully analyze the choice of parameters in Eq.
{[}eq:advecPhi{]}.

@@

\leavevmode\hypertarget{ref-wang2013modelling}{}%
{[}34{]} Wang Y, Chen J, Larachi F. Modelling and simulation of
trickle-bed reactors using computational fluid dynamics: A
state-of-the-art review. The Canadian Journal of Chemical Engineering
2013;91:136--80.

\leavevmode\hypertarget{ref-Whitaker2013}{}%
{[}35{]} Whitaker S. The method of volume averaging. vol. 13. Springer
Science \& Business Media; 2013.

\leavevmode\hypertarget{ref-saffman1958penetration}{}%
{[}36{]} Saffman PG, Taylor GI. The penetration of a fluid into a porous
medium or hele-shaw cell containing a more viscous liquid. Proceedings
of the Royal Society of London Series A Mathematical and Physical
Sciences 1958;245:312--29.

\leavevmode\hypertarget{ref-park1984two}{}%
{[}37{]} Park C-W, Homsy G. Two-phase displacement in hele shaw cells:
Theory. Journal of Fluid Mechanics 1984;139:291--308.

\leavevmode\hypertarget{ref-jackson2015dynamic}{}%
{[}38{]} Jackson S, Stevens D, Giddings D, Power H. Dynamic-wetting
effects in finite-mobility-ratio hele-shaw flow. Physical Review E
2015;92:023021.

\leavevmode\hypertarget{ref-Olsson2005}{}%
{[}39{]} Olsson E, Kreiss G. A conservative level set method for two
phase flow. Journal of Computational Physics 2005;210:225--46.
\url{https://doi.org/https://doi.org/10.1016/j.jcp.2005.04.007}.

\leavevmode\hypertarget{ref-Olsson2007}{}%
{[}40{]} Olsson E, Kreiss G, Zahedi S. A conservative level set method
for two phase flow ii. Journal of Computational Physics
2007;225:785--807.
\url{https://doi.org/https://doi.org/10.1016/j.jcp.2006.12.027}.

\leavevmode\hypertarget{ref-Popinet2018}{}%
{[}41{]} Popinet S. Numerical models of surface tension. Annual Review
of Fluid Mechanics 2018;50:49--75.
\url{https://doi.org/10.1146/annurev-fluid-122316-045034}.

\leavevmode\hypertarget{ref-Galusinski2008}{}%
{[}42{]} Galusinski C, Vigneaux P. On stability condition for bifluid
flows with surface tension: Application to microfluidics. Journal of
Computational Physics 2008;227:6140--64.
\url{https://doi.org/https://doi.org/10.1016/j.jcp.2008.02.023}.

>>>>

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdftitle={Numerical investigation of two-phase flow in high-permeability porous media Effect of permeability variation on the surface force between phases},
            pdfauthor={Maxime Cochennec¹; Hossein Davarzani¹* (h.davarzani@brgm.fr); Yohan Davit²; Ioannis Ignatiadis¹; Michel Quintard²},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
% Fix footnotes in tables (requires footnote package)
\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{longtable}}{}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\title{Numerical investigation of two-phase flow in high-permeability porous
media Effect of permeability variation on the surface force between
phases}
\author{Maxime Cochennec¹ \and Hossein Davarzani¹* (h.davarzani@brgm.fr) \and Yohan Davit² \and Ioannis Ignatiadis¹ \and Michel Quintard²}
\date{\today{}}

@@

The macroscopic description of two-phase flow in porous media requires
modeling the force of interaction between the phases, i.e.~the two
fluids and the solid phase. The flow regimes specific to high
permeability porous media are characterized by a non-negligible extent
of the interface between the two fluids, compared to the fluid-solid
interface. This argues for the systematic introduction of the
fluid-fluid interaction terms, the traction, in the macroscopic momentum
equations. However, we do not know whether these terms are always
non-negligible for this type of flow regime, for example in cases where
the friction with the solid becomes very large. Here we show that the
share of the traction between the fluids in the overall pressure drop
increases when the flow is more confined, and thus the friction with the
solid phase increases. The idea of solving modified 2D-Stokes equations
with a supplementary Darcy term allowed us to modify the intrinsic
permeability of the structure without having to modify the geometry per
se. Our results demonstrate that the absolute permeability of the
structure does not prejudge the importance of the traction between
fluids in the total pressure drop as long as the flow regime is
characteristic of flow in high permeability porous media.

@@

where the relative velocity is given by \(U_r=U_g-\frac{S_g}{S_l}U_l\)
and \(A_{lg}\) and \(B_{lg}\) are coefficients that depend on the volume
fraction of the gas phase and the medium properties. The subscripts
\(g\) and \(l\) denote the gas phase and the liquid phase, respectively.
This type of model with explicit account of interaction between fluids,
see also
{[}\protect\hyperlink{ref-tung1988hydrodynamic}{33},\protect\hyperlink{ref-iliuta2005modelling}{34}{]},
gives good results when compared with experimental results
{[}\protect\hyperlink{ref-wang2013modelling}{35}{]}.

@@

Up to this point we have seen that the macroscopic momentum equations
need the modeling of the force of interaction terms between phases. The
interaction between fluids is neglected in the traditional model used
for the study of subsurface two-phase flow, while it has been
experimentally observed that these terms are important when studying
two-phase flow in high permeability porous media. However, it is not
known whether these terms are always important when the extent of the
interface between the fluids is important. For example, do they become
negligible when friction with the solid phase increases? To what extent?
To answer this question, we performed direct numerical simulations of
two-phase flow in a Hele-Shaw cell as a model high permeability porous
medium. We solved a coupled Level-Set and Stokes equations with an
additional Darcy-term in the momentum equation that pertain for the
absolute permeability of the flow between two plates. Thus, the friction
due to the solid walls is increased by decreasing the aperture between
the cell plates. This paper discusses the value of the interaction terms
as a function of the aperture between the plates, i.e.~the absolute
permeability of the medium, and the capillary number.

@@

As said, an essential step in order to derive some macroscopic law at
macroscale from the microscale is to use averaged quantities to express
the boundary integrals terms that arising because of the averaging
theorem application {[}\protect\hyperlink{ref-Whitaker2013}{36}{]}.
Remember that these closure relations are not presented here but rather
we leave intact the surface integrals, the averaged momentum balance
equations +\textbf{???} for two fluids \(w\) and \(o\), are recast as

@@

\[
w=-\frac{1}{2\mu}\frac{dp}{dx}z(z-h).
\] \{\#eq:poiseuilleProfile\}

@@

There is therefore a direct analogy between flows in a 2D porous medium
and flow in a Hele-Shaw cell, as can be seen in +\textbf{???}, where the
permeability is given by \(h^{2}/12\)
{[}\protect\hyperlink{ref-saffman1958penetration}{37}{]}.

@@

where \(\gamma\) denotes the surface tension and \(\kappa_{\parallel}\)
the curvature in the Hele-Shaw plane
{[}\protect\hyperlink{ref-saffman1958penetration}{37}{]}. The
+\textbf{???} was completed in
{[}\protect\hyperlink{ref-park1984two}{38}{]} by an additional term that
pertains for dynamic film formation and a corrective \(\pi/4\) factor
for the curvature in the cell plane. The reader is warnes that while
dynamic film formation along the plates is an important phenomenom
regarding the flow {[}\protect\hyperlink{ref-jackson2015dynamic}{39}{]},
this requires dedicated study and is beyond the scope of this article.
Thus, we consider in the following that the invading fluid is in contact
with the cell plates, i.e.~presence of a triple line.

@@

In this equation, \(\mathbf{u}\) is the velocity field, \(\tau\) and
\(\psi\) are two numerical parameters that control the diffuse interface
thickness and the amount of reinitialization of the \(\phi\) function,
respectively
{[}\protect\hyperlink{ref-Olsson2005}{40},\protect\hyperlink{ref-Olsson2007}{41}{]}.

@@

where \(k=\frac{\sqrt{12}}{h}\) is an additional term that pertain to a
Darcy-term arising from the depth-averaging of the Stokes equation, as
described in the theoretical background section and \(\mathbf{F}_{st}\)
is the capillary contribution. The capillary contribution is difficult
to compute in volumetric methods such as Level Set and is itself the
object of a large body of work
{[}\protect\hyperlink{ref-Popinet2018}{42}{]}, this term is defined here
as

@@

where \(\gamma\) is the surface tension, \(\kappa\) is the interface
mean curvature, \(\mathbf{n}\) denotes the unit normal to the interface
and \(\delta(\phi)\) is the Dirac delta function localized on the
interface {[}\protect\hyperlink{ref-Galusinski2008}{43}{]}. In this
framework the unit normal vector as well as the mean curvature are
obtained with the level set function \(\phi\) as

@@

respectively, where the \(\pi/4\) correction was derived in
{[}\protect\hyperlink{ref-park1984two}{38}{]} and
\(\kappa_{\perp}=\frac{2}{h}\) is the out-of-plane curvature as
described previously in the theoretical background section.

@@

Let us now sum up all the traction terms and answer the question of the
share of traction exerted on the fluid-fluid boundary in total traction.
The traction exerted on the fluid-fluid boundary reaches between 10 and
50\% of the traction exerted on the solid-fluid boundaries, as can be
seen in \cref{fig:ratioDrag}, on which we plot the ratio
\(T_int^x/T_s^x\) as a function of the dimensionless aperture between
the cell plates. Interestingly, the ratio varies non-monotonically with
\(h^*\), the minimum is reached for the smallest tested capillary
numbers and a medium range of the aperture values. Logically the
traction at the interface between the fluids is important when the
aperture between the plates is maximum (the solution tends towards the
2D solution). For a moderate aperture, the proportion of traction at the
fluid-fluid interface decreases then rises again as the opening and thus
the absolute permeability of the cell decreases.

The variation of the ratio strongly depends on the capillary number and
that the smaller the capillary number, the smaller the traction at the
fluid interface. This is clearly visible in \cref{fig:ratioDragCa} on
which we plot the ratio \(T_int^x/T_s^x\) as a function of the capillary
number for different values of the opening between the plates.

@@

\begin{figure}
\hypertarget{fig:ratioDragCa}{%
\centering
\includegraphics{figures/pdf/ratioDragCa.pdf}
\caption{Ratio of traction (\(x\)-component) on fluid-fluid interface
over traction on solid-fluid interfaces in UC3 as a function of the
capillary number and for different apertures at
steady-state.}\label{fig:ratioDragCa}
}
\end{figure}

@@

We investigated the effect of varied permeability on cocurrent two-phase
flow in a Hele-Shaw cell. We focused on the value of the traction terms,
that are necessary to close the macroscopic flow equations. The idea of
solving modified 2D-Stokes equations with a supplementary Darcy term
allowed us to modify the intrinsic permeability of the structure without
having to modify the geometry per se. The range of intrinsic
permeability values investigated is typical of high-permeability porous
media, for which it is known that the flow regimes are characterized by
the large extent of the fluid-fluid interface (e.g.~film flow). With
direct numerical simulations we found that

@@

The code is validated by comparison with a Boundary-Element Method,
which relies on a surface discretization of the interface and a
pseudo-analytical formulation in the bulk of the phases. This allows us
to precisely locate the interface, even in the case of very thin film
flow, and to carefully analyze the choice of parameters in the transport
equation.

@@

\leavevmode\hypertarget{ref-iliuta2005modelling}{}%
{[}34{]} Iliuta I, Larachi F. Modelling the hydrodynamics of gas-liquid
packed beds via slit models: A review. International Journal of Chemical
Reactor Engineering 2005;3.

\leavevmode\hypertarget{ref-wang2013modelling}{}%
{[}35{]} Wang Y, Chen J, Larachi F. Modelling and simulation of
trickle-bed reactors using computational fluid dynamics: A
state-of-the-art review. The Canadian Journal of Chemical Engineering
2013;91:136--80.

\leavevmode\hypertarget{ref-Whitaker2013}{}%
{[}36{]} Whitaker S. The method of volume averaging. vol. 13. Springer
Science \& Business Media; 2013.

\leavevmode\hypertarget{ref-saffman1958penetration}{}%
{[}37{]} Saffman PG, Taylor GI. The penetration of a fluid into a porous
medium or hele-shaw cell containing a more viscous liquid. Proceedings
of the Royal Society of London Series A Mathematical and Physical
Sciences 1958;245:312--29.

\leavevmode\hypertarget{ref-park1984two}{}%
{[}38{]} Park C-W, Homsy G. Two-phase displacement in hele shaw cells:
Theory. Journal of Fluid Mechanics 1984;139:291--308.

\leavevmode\hypertarget{ref-jackson2015dynamic}{}%
{[}39{]} Jackson S, Stevens D, Giddings D, Power H. Dynamic-wetting
effects in finite-mobility-ratio hele-shaw flow. Physical Review E
2015;92:023021.

\leavevmode\hypertarget{ref-Olsson2005}{}%
{[}40{]} Olsson E, Kreiss G. A conservative level set method for two
phase flow. Journal of Computational Physics 2005;210:225--46.
\url{https://doi.org/https://doi.org/10.1016/j.jcp.2005.04.007}.

\leavevmode\hypertarget{ref-Olsson2007}{}%
{[}41{]} Olsson E, Kreiss G, Zahedi S. A conservative level set method
for two phase flow ii. Journal of Computational Physics
2007;225:785--807.
\url{https://doi.org/https://doi.org/10.1016/j.jcp.2006.12.027}.

\leavevmode\hypertarget{ref-Popinet2018}{}%
{[}42{]} Popinet S. Numerical models of surface tension. Annual Review
of Fluid Mechanics 2018;50:49--75.
\url{https://doi.org/10.1146/annurev-fluid-122316-045034}.

\leavevmode\hypertarget{ref-Galusinski2008}{}%
{[}43{]} Galusinski C, Vigneaux P. On stability condition for bifluid
flows with surface tension: Application to microfluidics. Journal of
Computational Physics 2008;227:6140--64.
\url{https://doi.org/https://doi.org/10.1016/j.jcp.2008.02.023}.
